### 2013-04-11 MSteenhagen-CV.tex
Some punctuation

\noindent\emph{University College London \vspace{0.01in}}

\ind Doctoral Candidate (PhD) in Philosophy.

\ind Dissertation on the perceptual nature of pictorial representation.\\ Supervisor: Prof. Mark Eli Kalderon.

@@

\ind Philosophy of psychology; Philosophy of perception; Aesthetics.

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language.

@@

\noindent\emph{University College London, Department of  Philosophy \vspace{0.01in}}

@@

\ind 2011. MPhil Stud., Philosophy. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.\\ Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

\noindent\emph{University of Utrecht, Department of  Philosophy\vspace{0.02in}}

\ind 2009. B.A., Philosophy.

@@

\noindent\emph{ArtEZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}

\ind 2005. BFA., Fine Art.

@@

@@

\marginhead{Teaching experience}

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Talks (recent)}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

\ind 2012. ``Two problems of co-consciousness.'' Department of Philosophy, University of Warwick, \href{http://www2.warwick.ac.uk/fac/soc/philosophy/news/conferences/mindgrad-2012/}{MindGrad 2012}. Respondent: Dr. Christoph Hoerl (Warwick).

@@

%\end{revnumerate}
\bigskip

@@

\marginhead{{\vskip 0.4em}Grants and \newline Awards}
\medskip

\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)

\marginhead{{\vskip 0.9em}Work experience}
\medskip

>>>>

\ind Doctoral Candidate (PhD) in Philosophy, \emph{University College London \vspace{0.01in}}

\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon

@@

\ind Philosophy of psychology; Philosophy of perception; Aesthetics

@@

\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language

@@

@@

\ind 2011. MPhil Stud., Philosophy. Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}. \emph{University College London, Department of  Philosophy \vspace{0.01in}}\\ Supervisors: Prof. Mark Eli Kalderon; Prof. Christopher Peacocke. \vspace{-0.1in}

@@

\ind 2009. B.A., Philosophy. \emph{University of Utrecht, Department of  Philosophy\vspace{0.02in}}

@@

\ind 2005. BFA., Fine Art. \emph{ArtEZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}

@@

\marginhead{{\vskip 0.4em}Scholarships \newline and awards}
\medskip

\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} Two-year PhD Studentship Award. %(£36.000)

@@

%\newpage
%% Presentations
\marginhead{{\vskip 0.4em}Research \newline presentations}
\medskip
\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)

@@

\ind 2012. ``Two problems of co-consciousness.'' Department of Philosophy, University of Warwick, \href{http://www2.warwick.ac.uk/fac/soc/philosophy/news/conferences/mindgrad-2012/}{MindGrad 2012}. Respondent: Dr Christoph Hoerl (Warwick).

@@

%\end{revnumerate}
\bigskip
\marginhead{Teaching experience}

@@

\marginhead{{\vskip 0.9em}Work \newline experience}
\medskip
